Refining from the BON High-level Specification Language to the VHDL Hardware Description Language

### 2009-07-25 papers/BON_VHDL/paper.tex
start paper work

The \STs have several unusual built-in sensors and emitters, sensor
nodes can be extended via a general-purpose USB bus, and \STs contain
an FPGA that is dynamically updated on a per-experiment basis.  \STs
are custom-designed in VHDL.  Like many hardware-based systems, to
write new software for or against the \ST architecture one either uses
the actual hardware or one runs a \STS.  But this simulator emulates a
piece of hardware, one would like to know if the simulator
\emph{actually} simulates the hardware.  We have developed an approach
through which we refine the VHDL specification up to the formal BON
specification language, and from this specification we generate an
executable, functional model-based specification in the JML language.
We have used this specification to implement a fully validated and
verified \ST simulator.

@@

%======================================================================
\section{Introduction}

An introduction.

>>>>

The \STs, as an embedded system, have several unusual built-in sensors 
and emitters, sensor nodes can be extended via a general-purpose USB bus, 
and \STs contain an FPGA that is dynamically updated on a per-experiment 
basis.  \STs are custom-designed in VHDL.  Like many hardware-based systems,
 to write new software for or against the \ST architecture one either uses
the actual hardware or one runs a \STS.  But this simulator emulates a
piece of hardware, one would like to know if the simulator
\emph{actually} simulates the hardware.  We have developed an approach
through which we refine the VHDL specification up to the formal BON
specification language, and from this specification we generate an
executable, functional model-based specification in the JML language.
We have used this specification to implement a fully validated and
verified \ST simulator.

@@

%======================================================================
\section{Introduction}
The Embedded system is composed of a heterogeneous collection of digital,
analog and mixed signal hardware components.The development of complex 
embedded system requires sophisticated tool and methodology in order to 
be able to complete a correct design in time. Embedded system complexity 
requires the need to strive for abstract specification and formal 
descriptions each component separatelly in order to produce formal 
specification of the whole system. The main goal is fast design approach 
in order to produce simulator and to minimize the time spent.

The \STs represents an embedded system designed in VHDL.

The authors will illustrate in this paper how BON can represent a high 
level analogue mapping and will further illustrate a procedure for 
transformation from BON to VHDL-ASM.
%=====================================================================

\section{VHDL-ASM}
\subsection{Hardware description language}

\section{Choice of BON as the modeling tool}
%Brief description and motivation.
The Business Object Notation (BON) is an analysis and design notation for 
object-oriented systems  which emphasizes \emph{seamlessness}, \emph{reversibility} and software \emph{contracting}.

\begin{itemize}
\item \emph{Seamlessness} is the use of a continuous process throughout the software lifecycle.
%\todo{dragan 25/07/2009 - Figure out relation: Seamlessness and VHDL-ASM}
\item \emph{Reversibility} is the support for both forward and backward engineering: from analysis to
design and implementation, and back.
%\todo{dragan 25/07/2009 - Figure out relation: Reversibility and VHDL-ASM. Why is Reversibility important in VHDL design.}
\item \emph{Contracting} is the precise definition, for each software element, of the associated semantic properties. 
BON is the only one among the popular analysis methods to use a full assertion
mechanism, allowing analysts to specify not only the structure of a system but also its
semantics ( preconditions, postconditions and invariants of the expected results ).
\end{itemize}

BON focuses on the fundamental elements of analysis and design, and the method is
meant to be integrated with and adapted to the various development frameworks
including embedded system.

Because of its flexibility, it is not difficult to find mappings into other domains
which would seem to indicate that object-oriented modeling is really equivalent
to process modeling with signal passing, or refinement of VHDL language.

Therefore as a distillation of best modelling practices, and as the 
language based on contract design and refinement calculus, BON
is the obvious choice for the current work.

\subsection{Mapping between BON and VHDL}
%\todo{dragan 25/07/2009 - Figure out : Mapping from BON  to entity/architecture structure in VHDL-ASM.}
\subsection{Adapting BON for VHDL modeling }

\section{Example}
